Research log

### 2023-05-11 docs/ExploratoryResults.Rmd
small formatting tweaks

author: 
  - name          : "Matan Mazor"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Malet St., London WC1E 7HX"
    email         : "mtnmzor@gmail.com"
  - name          : "Chaz Firestone"
    affiliation   : "2"
  - name          : "Ian Phillips"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Birkbeck, University of London"
  - id            : "2"
    institution   : "Johns Hopkins University"

@@

```{r half-games, echo=FALSE, out.width = '100%', fig.cap = "Half games. First column: the two boards, as they appeared to pretenders. Second column: objective hit probability, given game state. Third and fourth columns: empirical click probabilities in non-pretend and pretend games, respectively."}
knitr::include_graphics("figures/Half_games.png")
```

## Within-participant click entropy

@@

E4.misses_per_word %>%
  ggplot(aes(x=nonpretend,y=pretend, label=word)) +
  geom_abline(intercept=0,slope=1) +
  geom_point()+
  geom_text_repel()+
  coord_fixed(ratio=1)+
  scale_x_continuous(limits=c(0,5.5), breaks=seq(0,5))+
  scale_y_continuous(limits=c(0,5.5), breaks=seq(0,5)) +
  theme(legend.position = 'none')+
  theme_bw() +
  labs(title='number of misses')

@@

## Within-participant click entropy

>>>>

# author: 
#   - name          : "Matan Mazor"
#     affiliation   : "1"
#     corresponding : yes    # Define only one corresponding author
#     address       : "Malet St., London WC1E 7HX"
#     email         : "mtnmzor@gmail.com"
#   - name          : "Chaz Firestone"
#     affiliation   : "2"
#   - name          : "Ian Phillips"
#     affiliation   : "2"
# 
# affiliation:
#   - id            : "1"
#     institution   : "Birkbeck, University of London"
#   - id            : "2"
#     institution   : "Johns Hopkins University"

@@

```{r half-games, echo=FALSE, out.width = '100%', fig.cap = "Half games. First column: the two boards, as they appeared to pretenders. Second column: objective hit probability, given game state. Third and fourth columns: empirical click probabilities in non-pretend and pretend games, respectively."}
knitr::include_graphics("figures/Half_games.png")
```
## Heuristic use

In Battleship, players sometimes have a fixed sequence of clicks that they follow, at least for the first moves. To quantify this, we plot the distribution of the first 5 clicks from all all games of a random subset of 100 players:

```{r get-Battleship-prior, fig.cap="Distribution of the first 5 clicks in all games, from a subset of 100 random players"}

set.seed(42)
all_subjects <- E2.click_log$subj_id%>%unique();
random100 <- all_subjects[sample(length(all_subjects),100)]

E2.prior_first5 <- E2.click_log %>%
  filter(click_number<6 & subj_id %in% random100)%>%
  group_by(i,j)%>%
  summarise(n=n()) %>%
  mutate(p=n/sum(n),
         flat_position = 1+i*5+j)

ggplot(E2.prior_first5,aes(x=j,y=i,fill=p)) +
  geom_tile() +
  coord_equal() +
  scale_x_continuous(breaks=c()) +
  scale_y_continuous(breaks=c(),trans='reverse') +
  scale_fill_gradient(low='#649bc8',high='#c83237', na.value ='white')+
  labs(x='',y='') +
  theme_classic() +
  labs(title='click probability in Battleship')
```

As can be seen, subjects prefer to click on the diagonals, with a slight preference for the left hand side. We then asked how well aligned are players' clicks with this map in pretend and non-pretend games. For this analysis, we only used data from the remaining `r all_subjects%>%length()-random100%>%length()` players whose games were not used for generating the above map.

```{r battleship-prior-comparison}

battleship_prior <- E2.prior_first5$p;

get_p_heuristic_rank <- function(posterior, flat_position) {
  posterior <- scan(text= posterior, what = numeric(), sep="," , quiet = TRUE);
  prior = battleship_prior*posterior/posterior #to get rid of nans
  rank_prior = rank(-prior)
  return(rank_prior[flat_position])
}

E2.click_log_with_heuristic <- E2.click_log_with_boards %>%
  rbind(E2.click_log_with_boards_optimal) %>%
  rbind(E2.click_log_with_boards_random) %>%
  rowwise() %>%
  mutate(p_heuristic_rank = get_p_heuristic_rank(posterior,flat_position))

E2.mean_P_heuristic_rank <- E2.click_log_with_heuristic %>%
  filter(!(subj_id %in% random100))%>%
  group_by(subj_id,test_part) %>%
  summarise(p_heuristic_rank=mean(p_heuristic_rank))

E2.mean_P_heuristic_rank %>%
    filter(test_part != 'optimal') %>%
    ggplot(aes(x=p_heuristic_rank,fill=test_part))+
    geom_histogram( color="black", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
    labs(x='mean rank according to the above map', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    # facet_wrap(~genuine_first, nrow=2)+
    # scale_x_reverse() +
    theme_classic();

We find no difference in this measure between pretend and non-pretend games (`r E2.mean_P_heuristic_rank%>%spread(test_part,p_heuristic_rank)%>%mutate(diff=nonpretend-pretend)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`). In the next analysis we use a more sensitive, player-specific measure of players' tendency to follow a fixed heuristic, versus playing flexibly.

## Within-participant sequential guess entropy

@@

E4.misses_per_word %>%
  ggplot(aes(x=nonpretend,y=pretend, label=toupper(word))) +
  geom_abline(intercept=0,slope=1) +
  geom_point()+
  geom_text_repel()+
  coord_fixed(ratio=1)+
  scale_x_continuous(limits=c(0,5), breaks=seq(0,5))+
  scale_y_continuous(limits=c(0,5), breaks=seq(0,5)) +
  theme(legend.position = 'none')+
  theme_bw() +
  labs(x='median number of misses: non-pretend',
       y='median number of misses: pretend')

ggsave('figures/E4_scatter_misses.png',width=3.5, height=3.5)

@@

## Within-participant sequential guess entropy

### 2023-05-11 docs/preregisteredMethodsAndResults.Rmd
small formatting tweaks

We used `r cite_r("r-references.bib")` for all our analyses.

@@

```
### Model based analysis

@@

E2.mean_P_click_rank_misses_only <- E2.click_log_with_boards %>%
  rbind(E2.click_log_with_boards_optimal) %>%
  rbind(E2.click_log_with_boards_random) %>%
  rowwise() %>%
  filter(!hit_bin) %>%
  group_by(subj_id,test_part, genuine_first) %>%
  summarise(p_click_rank=mean(p_click_rank))

@@

p<- E2.mean_P_click_rank_misses_only %>%
    filter(test_part != 'optimal') %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
    labs(x='p(ship in clicked square) - rank', y='number of players')+
    scale_x_continuous(limits=c(0,15))+
    theme(legend.position=c(0.10,0.85)) +
    # facet_wrap(~genuine_first, nrow=2)+
    # scale_x_reverse() +
    theme_classic();

ggsave('figures/E2_pclick_rank_misses_only.pdf',p)
ggsave('figures/E2_pclick_rank_misses_only.png',p,width=5,height=2,dpi=300)

@@

The mean posterior rank of non-pretend cell selections was `r E2.mean_P_click_rank%>%filter(test_part=='nonpretend')%>%pull(p_click_rank)%>%mean()%>%printnum()` and significantly lower (more optimal) than that of a simulated random agent (`r E2.mean_P_click_rank%>%filter(test_part=='random')%>%pull(p_click_rank)%>%mean()%>%printnum()`, `r E2.mean_P_click_rank%>%spread(test_part,p_click_rank)%>%mutate(diff=nonpretend-random)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`). Pretend games were significantly less optimal than non-pretend games (`r E2.mean_P_click_rank%>%filter(test_part=='pretend')%>%pull(p_click_rank)%>%mean()%>%printnum()`; pretend-first group: `r E2.mean_P_click_rank%>%filter(!genuine_first)%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-nonpretend)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`; pretend-second group: `r E2.mean_P_click_rank%>%filter(genuine_first)%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-nonpretend)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`), but still more optimal than those of a random agent (`r E2.mean_P_click_rank%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-random)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`). Critically, the same pattern was observed when restricting analysis to cell selections that resulted in a miss (non-pretend - pretend: `r apa_print(t.test(E2.mean_P_click_rank_misses_only%>%filter(genuine_first&test_part=='nonpretend')%>%pull(p_click_rank), E2.mean_P_click_rank_misses_only%>%filter(!genuine_first&test_part=='pretend')%>%pull(p_click_rank)))$statistic`; pretend - random: `r E2.mean_P_click_rank_misses_only%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-random)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`). In other words, the optimality of pretend games relative to random cell selection was not merely due to the fact that pretenders clicked on ships more than expected by chance. Even when missing a ship, their cell selections made sense given the limited information they pretended to have.

@@

# E4.click_log_with_boards_optimal <- E4.click_log_with_boards %>%
#   mutate(letter = get_optimal_letter(posterior),
#          p_click = get_p_letter(posterior,letter),
#          p_click_rank = get_p_letter_rank(posterior,letter),
#          hit_bin = tolower(letter) %in% strsplit(tolower(word),'')[[1]],
#          test_part='most_frequent');

@@

# save(E4.click_log_with_boards,
#      E4.click_log_with_boards_random,
#      E4.click_log_with_boards_most_frequent,
#      E4.letter_prob_click_log_with_boards,
#      E4.letter_prob_click_log_with_boards_random,
#      file='E4.click_log_with_boards.RData')

@@

E4.mean_P_click_rank <- E4.click_log_with_boards %>%
  rbind(E4.click_log_with_boards_random)%>%
  group_by(subj_id,test_part, genuine_first) %>%
  summarise(p_click_rank=mean(p_click_rank))

@@

E4.mean_letter_prob_P_click_rank <- E4.letter_prob_click_log_with_boards %>%
  rbind(E4.click_log_with_boards_random)%>%
  group_by(subj_id,test_part, genuine_first) %>%
  summarise(p_click_rank=mean(p_click_rank))

@@

p<- E4.mean_P_click_rank %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( alpha=0.6, position = 'identity', nbins=100) +
    scale_fill_manual(values=c("#69b3a2", "#404080",  "#FDE725")) +
    labs(x='p(letter in word) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    facet_wrap(~genuine_first, nrow=2)+
    theme_classic();

@@

p<- E4.mean_letter_prob_P_click_rank %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( alpha=0.6, position = 'identity', nbins=100) +
    scale_fill_manual(values=c("#69b3a2", "#404080",  "#FDE725")) +
    labs(x='p(letter) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    facet_wrap(~genuine_first, nrow=2)+
    theme_classic();

@@

E4.mean_P_click_rank_misses <- E4.click_log_with_boards %>%
  filter(!hit_bin) %>%
  rbind(E4.click_log_with_boards_random %>%filter(!hit_bin))%>%
  group_by(subj_id,test_part, genuine_first) %>%
  summarise(p_click_rank=mean(p_click_rank))

@@

p<- E4.mean_P_click_rank_misses %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( alpha=0.6, position = 'identity', nbins=100) +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
    labs(x='p(letter in word) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    facet_wrap(~genuine_first, nrow=2)+
    theme_classic();

@@

p<- E4.mean_letter_prob_P_click_rank_misses %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( alpha=0.6, position = 'identity', nbins=100) +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
    labs(x='p(letter) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    facet_wrap(~genuine_first, nrow=2)+
    theme_classic();

@@

p <- E4.rank_misses_by_category %>% ggplot(
  aes(x=as.factor(word),y=p_rank,fill=test_part)
) + 
  geom_bar(position=position_dodge(),
           stat='identity', color='black')+
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
  geom_errorbar(aes(ymin=p_rank-se, ymax=p_rank+se), width=.2,position=position_dodge(.9)) +
  labs(x='word',
       y='posterior rank')

@@

E4.mean_P_click_rank %>%
    filter(test_part != 'optimal') %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( color="black", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
    labs(x='p(letter in word) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    # facet_wrap(~genuine_first, nrow=2)+
    # scale_x_reverse() +
    theme_classic();

@@

E4.mean_letter_prob_P_click_rank %>%
    filter(test_part != 'optimal') %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( color="black", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
    labs(x='p(letter in English text) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    # facet_wrap(~genuine_first, nrow=2)+
    # scale_x_reverse() +
    theme_classic();

@@

E4.letter_choice_frequency <- E4.half_game_click_log %>%
  filter(click_number==1) %>%
  dplyr::select(subj_id,test_part,word_state,letter) %>%
  mutate(letter=factor(letter,levels=toupper(letters))) %>%
  group_by(letter,test_part,word) %>%
  summarise(count = n()) %>%
  group_by(test_part,word) %>%
  mutate(p=count/sum(count)) %>%
  complete(letter,fill=list(count=0,p=0)) %>%
  mutate(test_part=ifelse(test_part=='pretend_half_game','pretend','non-pretend'))

E4.letter_choice_frequenc_wide <- E4.letter_choice_frequency %>%
  dplyr::select(-count, -word_state) %>% 
  spread(letter,p)

@@

>>>>

<!-- We used `r cite_r("r-references.bib")` for all our analyses. -->

@@

@@

E2.mean_P_click_rank_misses <- E2.click_log_with_boards %>%
  rbind(E2.click_log_with_boards_optimal) %>%
  rbind(E2.click_log_with_boards_random) %>%
  rowwise() %>%
  filter(!hit_bin) %>%
  group_by(subj_id,test_part, genuine_first) %>%
  summarise(p_click_rank=mean(p_click_rank))

@@

p<- E2.mean_P_click_rank_misses %>%
    filter(test_part != 'optimal') %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
    labs(x='p(ship in clicked square) - rank', y='number of players')+
    scale_x_continuous(limits=c(0,15))+
    theme(legend.position=c(0.10,0.85)) +
    # facet_wrap(~genuine_first, nrow=2)+
    # scale_x_reverse() +
    theme_classic();

ggsave('figures/E2_pclick_rank_misses.pdf',p)
ggsave('figures/E2_pclick_rank_misses.png',p,width=5,height=2,dpi=300)

@@

The mean posterior rank of non-pretend cell selections was `r E2.mean_P_click_rank%>%filter(test_part=='nonpretend')%>%pull(p_click_rank)%>%mean()%>%printnum()` and significantly lower (more optimal) than that of a simulated random agent (`r E2.mean_P_click_rank%>%filter(test_part=='random')%>%pull(p_click_rank)%>%mean()%>%printnum()`, `r E2.mean_P_click_rank%>%spread(test_part,p_click_rank)%>%mutate(diff=nonpretend-random)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`). Pretend games were significantly less optimal than non-pretend games (`r E2.mean_P_click_rank%>%filter(test_part=='pretend')%>%pull(p_click_rank)%>%mean()%>%printnum()`; pretend-first group: `r E2.mean_P_click_rank%>%filter(!genuine_first)%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-nonpretend)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`; pretend-second group: `r E2.mean_P_click_rank%>%filter(genuine_first)%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-nonpretend)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`), but still more optimal than those of a random agent (`r E2.mean_P_click_rank%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-random)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`). Critically, the same pattern was observed when restricting analysis to cell selections that resulted in a miss (non-pretend - pretend: `r apa_print(t.test(E2.mean_P_click_rank_misses%>%filter(genuine_first&test_part=='nonpretend')%>%pull(p_click_rank), E2.mean_P_click_rank_misses%>%filter(!genuine_first&test_part=='pretend')%>%pull(p_click_rank)))$statistic`; pretend - random: `r E2.mean_P_click_rank_misses%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-random)%>%pull(diff)%>%t.test()%>%apa_print()%>%'$'(statistic)`). In other words, the optimality of pretend games relative to random cell selection was not merely due to the fact that pretenders clicked on ships more than expected by chance. Even when missing a ship, their cell selections made sense given the limited information they pretended to have.

@@

# E4.click_log_with_boards_optimal <- E4.click_log_with_boards %>%
#   mutate(letter = get_optimal_letter(posterior),
#          p_click = get_p_letter(posterior,letter),
#          p_click_rank = get_p_letter_rank(posterior,letter),
#          hit_bin = tolower(letter) %in% strsplit(tolower(word),'')[[1]],
#          test_part='optimal');

@@

# E4.letter_prob_click_log_with_boards_optimal <- E4.letter_prob_click_log_with_boards %>%
#   dplyr::select(subj_id,genuine_first,test_part,word,category,word_state,click_number,posterior) %>%
#   left_join(E4.click_log_with_boards_optimal %>%
#               ungroup()%>%
#               dplyr::select(subj_id,word,click_number,letter,hit_bin),
#             by=c('subj_id','word','click_number')) %>%
#   mutate(p_click = get_p_letter(posterior,letter),
#          p_click_rank = get_p_letter_rank(posterior,letter),
#          hit_bin = tolower(letter) %in% strsplit(tolower(word),'')[[1]],
#          test_part='optimal');

# save(E4.click_log_with_boards, E4.click_log_with_boards_random,
# E4.click_log_with_boards_most_frequent, E4.click_log_with_boards_optimal,
# E4.letter_prob_click_log_with_boards,
# E4.letter_prob_click_log_with_boards_random,
# E4.letter_prob_click_log_with_boards_optimal,
# file='E4.click_log_with_boards.RData')

@@

E4.mean_P_click_rank <- E4.click_log_with_boards %>%
  rbind(E4.click_log_with_boards_random)%>%
  rbind(E4.click_log_with_boards_optimal)%>%
  group_by(subj_id,test_part, genuine_first) %>%
  summarise(p_click_rank=mean(p_click_rank))

@@

E4.mean_letter_prob_P_click_rank <- E4.letter_prob_click_log_with_boards %>%
  dplyr::select(subj_id,genuine_first, test_part,word,p_click_rank)%>%
  rbind(E4.letter_prob_click_log_with_boards_random%>%
    dplyr::select(subj_id,genuine_first, test_part,word,p_click_rank))%>%
  rbind(E4.letter_prob_click_log_with_boards_optimal %>%
    dplyr::select(subj_id,genuine_first, test_part,word,p_click_rank))%>%
  group_by(subj_id,test_part, genuine_first) %>%
  summarise(p_click_rank=mean(p_click_rank))

@@

p<- E4.mean_P_click_rank %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( alpha=0.6, position = 'identity', nbins=100) +
    scale_fill_manual(values=c("#69b3a2", "#404080",  "#FDE725", 'black')) +
    labs(x='p(letter in word) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    facet_wrap(~genuine_first, nrow=2)+
    theme_classic();

@@

p<- E4.mean_letter_prob_P_click_rank %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( alpha=0.6, position = 'identity', nbins=100) +
    scale_fill_manual(values=c("#69b3a2", "#404080",  "#FDE725", 'black')) +
    labs(x='p(letter) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    facet_wrap(~genuine_first, nrow=2)+
    theme_classic();

@@

E4.mean_P_click_rank_misses <- E4.click_log_with_boards %>%
  filter(!hit_bin) %>%
  rbind(E4.click_log_with_boards_random %>%filter(!hit_bin))%>%
  rbind(E4.click_log_with_boards_optimal %>%filter(!hit_bin))%>%
  group_by(subj_id,test_part, genuine_first) %>%
  summarise(p_click_rank=mean(p_click_rank))

@@

p<- E4.mean_P_click_rank_misses %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( alpha=0.6, position = 'identity', nbins=100) +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", 'black')) +
    labs(x='p(letter in word) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    facet_wrap(~genuine_first, nrow=2)+
    theme_classic();

@@

p<- E4.mean_letter_prob_P_click_rank_misses %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( alpha=0.6, position = 'identity', nbins=100) +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", 'black')) +
    labs(x='p(letter) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    facet_wrap(~genuine_first, nrow=2)+
    theme_classic();

@@

p <- E4.rank_misses_by_category %>% ggplot(
  aes(x=as.factor(word),y=p_rank,fill=test_part)
) + 
  geom_bar(position=position_dodge(),
           stat='identity', color='black')+
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", 'black')) +
  geom_errorbar(aes(ymin=p_rank-se, ymax=p_rank+se), width=.2,position=position_dodge(.9)) +
  labs(x='word',
       y='posterior rank')

@@

E4.mean_P_click_rank %>%
    filter(test_part != 'optimal') %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( color="black", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", 'black')) +
    labs(x='p(letter in word) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    # facet_wrap(~genuine_first, nrow=2)+
    # scale_x_reverse() +
    theme_classic();

@@

E4.mean_letter_prob_P_click_rank %>%
    filter(test_part != 'optimal') %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( color="black", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", 'black')) +
    labs(x='p(letter in English text) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    # facet_wrap(~genuine_first, nrow=2)+
    # scale_x_reverse() +
    theme_classic();

@@

E4.letter_choice_frequency <- E4.half_game_click_log %>%
  filter(click_number==1) %>%
  dplyr::select(subj_id,test_part,letter) %>%
  mutate(letter=factor(letter,levels=toupper(letters))) %>%
  group_by(letter,test_part,word) %>%
  summarise(count = n()) %>%
  group_by(test_part,word) %>%
  mutate(p=count/sum(count)) %>%
  complete(letter,fill=list(count=0,p=0)) %>%
  mutate(test_part=ifelse(test_part=='pretend_half_game','pretend','non-pretend'))

E4.letter_choice_frequenc_wide <- E4.letter_choice_frequency %>%
  dplyr::select(-count) %>% 
  spread(letter,p)

@@

p <- E4.letter_choice_frequency %>% 
  filter(test_part %in% c('pretend','non-pretend') & word %in% c('papaya','banana')) %>%
  mutate(letter = ifelse(letter %in% c('B','N','P','Y'), letter, 'other')) %>%
  mutate(letter = factor(letter, levels=c('B', 'N', 'P', 'Y','other')))%>%
  group_by(test_part,word,letter) %>%
  summarise(p=sum(p)) %>%
  mutate(test_part = factor(test_part, levels=c('non-pretend','pretend'))) %>%
  mutate(word = factor(word, levels=c('banana','papaya'), labels=c('BANANA','PAPAYA')))%>%
  ggplot(aes(x=reorder(letter, desc(letter)),y=p, fill=reorder(word, desc(word)))) +
  geom_bar(stat='identity', position='dodge') +
  facet_grid(cols=vars(test_part)) +
  theme_classic() +
  scale_fill_manual(values=c("#f16154","#fed601")) +
  labs(x='',y='frequency') +
  coord_flip() +
  theme(legend.pos='na')

ggsave('figures/Hangman2/bananapapaya.png',p,width=4,height=1.8,dpi=300)

p <- E4.letter_choice_frequency %>% 
  filter(test_part %in% c('pretend','non-pretend') & word %in% c('hair','hand')) %>%
  mutate(letter = ifelse(letter %in% c('N','D','I','R'), letter, 'other')) %>%
  mutate(letter = factor(letter, levels=c('N', 'D', 'I', 'R','other')))%>%
  group_by(test_part,word,letter) %>%
  summarise(p=sum(p)) %>%
  mutate(test_part = factor(test_part, levels=c('non-pretend','pretend'))) %>%
  mutate(word = factor(word, levels=c('hand','hair'), labels=c('HAND','HAIR')))%>%
  ggplot(aes(x=reorder(letter, desc(letter)),y=p, fill=reorder(word, desc(word)))) +
  geom_bar(stat='identity', position='dodge') +
  facet_grid(cols=vars(test_part)) +
  theme_classic() +
  scale_fill_manual(values=c("#9a3300","#f1c27d")) +
  labs(x='',y='frequency') +
  coord_flip() +
  theme(legend.pos='na')

ggsave('figures/Hangman2/handhair.png',p,width=4,height=1.8,dpi=300)
